Supplemental Materials: \\ \emph{Active-contours driven registration method for structure-informed segmentation of diffusion MR images}

### 2015-04-08 Publications/2015-NeuroImage/05-results.tex
updating supplementals

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-b}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

@@

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-a}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-b}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{A. Example of one report for visual assessment, automatically generated by the evaluation instrument.
    Each view shows one component of the input image (in this case, the \gls*{fa} map), the ground-truth location
    of the surfaces (green contours), and the resulting surfaces with the method under test (yellow contours).
  First two rows show axial slices for \emph{regseg} and the \acrfull*{t2b} method, and the last two rows
    show corresponding sagittal views.
  Coronal view is omitted since it is the least informative due to the the directional property
    of distortions.
	Red arrows point to regions where \emph{regseg} overperformed the \gls*{t2b} method.
  B. Violin plots of error distributions of each surface, with indication of the voxel size of the \gls*{dmri} images
    (1.25 mm), and supporting the improved results of \emph{regseg} in the proposed settings.
	}\label{fig:results_real}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05A}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05B}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

@@

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure06A}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure06B}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{A. Example of one report for visual assessment, automatically generated by the evaluation instrument.
    Each view shows one component of the input image (in this case, the \gls*{fa} map), the ground-truth location
    of the surfaces (green contours), and the resulting surfaces with the method under test (yellow contours).
  First two rows show axial slices for \emph{regseg} and the \acrfull*{t2b} method, and the last two rows
    show corresponding sagittal views.
  Coronal view is omitted since it is the least informative due to the the directional property
    of distortions.
	Red arrows point to regions where \emph{regseg} overperformed the \gls*{t2b} method.
  B. Violin plots of error distributions of each surface, with indication of the voxel size of the \gls*{dmri} images
    (1.25 mm), and supporting the improved results of \emph{regseg} in the proposed settings.
	}\label{fig:results_real}
\end{figure*}

### 2015-04-08 Publications/2015-NeuroImage/supplemental.tex
updating supplementals

% @Author: Oscar Esteban
% @Date:   2015-02-20 15:40:09
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-03-26 17:57:06

@@

% *** GRAPHICS RELATED PACKAGES ***
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{ifpdf}
\graphicspath{{figures/},{../Figures/}}

@@

% *** FLOAT PACKAGES ***
\usepackage[framemethod=tikz]{mdframed}
%\usepackage{float}
% \usepackage{fixltx2e}
% \usepackage{stfloats}
% \usepackage{dblfloatfix}

@@

\usepackage[hyphens]{url}
\usepackage[hyphenbreaks]{breakurl} %fixes boxes spanning through pages
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

@@

\begin{document}
\title{Supplemental Materials: \emph{Simultaneous segmentation and registration of
diffusion MR images of the brain driven by active-contours}}
\author{Oscar Esteban and Dominique Zosso}
\date{February 2015}

@@

\subsection{Gradient-descent optimization}\label{sec:gradient_descent}
The energy functional to be optimized
  in \emph{regseg} is presented in Eq. 7:
  \begin{equation}
  E(R \mid U) = C + \underbracket{\underset{l}{\sum} \int_{\Omega_l}
  \mdist{f'}{l} \,d\vec{r}}_{\text{Data term } (E_{data})}
  + \underbracket{\underset{\Omega}{\int} \left[ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} \right] \,d\vec{r}}_{\text{Regularization term } (E_{reg})}.
  \label{eq:energy}
  \end{equation}

To search for the minimum of $E(R \mid U)$ w.r.t. the coefficients $\vec{u}_k$, we use a gradient descent strategy.
In Eq. 11 we introduced the derivative of \eqref{eq:energy}:
  \begin{equation}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} =
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \underset{l}{\sum} \int_{\Omega_l} \mdist{f'}{l} \,d\vec{r}
  + \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\}.
  \label{eq:gradient_descent}
  \end{equation}

@@

It is also necessary to obtain and discretize the derivatives of the regularization term of \eqref{eq:gradient_descent}:
  \begin{equation}
  \frac{\partial E_{reg}(\vec{u})}{\partial \vec{u}_k} = \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\} = \boldsymbol{\alpha} \cdot \vec{u}_k + \boldsymbol{\beta} \cdot \Delta \vec{u}_k.
  \label{eq:gradient_regterm}
  \end{equation}

Inserting \eqref{eq:shape_gradient_final} and \eqref{eq:gradient_regterm} into \eqref{eq:gradient_descent} we get the
  final evolution equation:
  \begin{equation}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} = \vec{g}_k + \boldsymbol{\alpha} \cdot \vec{u}_k + \boldsymbol{\beta} \cdot \Delta \vec{u}_k,
  \label{eq:gradient_final}
  \end{equation}

\subsection{Obtaining the update equation} To solve the differential equation in \eqref{eq:gradient_descent},
  we use a semi-implicit Euler scheme, referring to the discrete step size as $\delta$ and where the
  shape-gradients $\vec{g}_k$ are explicit:
\begin{align}
  \vec{u}_k^{t+1} &= \vec{u}_k^{t} + \delta \, \Big( \vec{g}_k^{t+1} + (\boldsymbol{\alpha} - \boldsymbol{\beta} \Delta) \, \vec{u}_k^{t+1} \Big) \notag \\
  (1 - \delta \boldsymbol{\alpha} - \delta \boldsymbol{\beta} \Delta)\, \vec{u}_k^{t+1} &= \vec{u}_k^{t} + \delta\, \vec{g}_k^{t}
  \label{eq:discrete_derivative}
\end{align}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t + \vec{g}_k\} }%
                  {\mathcal{F}\{(\delta^{-1} - \boldsymbol{\alpha})\, I-\boldsymbol{\beta}\Delta\}} \right\},
  \label{eq:update_equation}
  \end{align}
  where $I$ denotes the identity operator.
Here, we rewrite the Laplacian as a linear combination of the identity and shift operators:
  \begin{equation}
  \Delta = \{\sum_{d=1}^n \mathcal{S}_d^- + \mathcal{S}_d^+\}  - 2n \mathcal{I}
  \end{equation}
  where $\mathcal{S}_d^{\pm}$ stands for the forward ($+$) and backward ($-$) shift operator along axis $d$, of which the Fourier transform is found easily as
  \begin{equation}
  \mathcal{F}\{\mathcal{S}_d^{\pm}\} = e^{\pm i\omega_d},
  \end{equation}
  where $\omega_d$ is the normalized pulsation along direction $d$.
Accordingly, the Fourier transform of the discrete Laplacian is found as
  \begin{align}
  \mathcal{F}\{\Delta\} &= \sum_d e^{-i\omega_d} + e^{i\omega_d} - 2n = n \, \left( \sum_d \cos(\omega_d) - 2\, \right)
  \end{align}

@@

\section{Parameter settings and implementation details of \emph{regseg}}

@@

@@

\begin{figure*}[b]
  \includegraphics[width=\textwidth]{figures/Suppl-figure02.pdf}
  \caption{The evolution of the registration and segmentation process can be
    checked using the \emph{Convergence report},
    easily generated using the appropriate \emph{nipype Interface}.
  The report comprehends several plots tracking the evolution of the algorithm and several
    features to help researchers tune up the algorithm in their application.}%
    \label{fig:convreport}
\end{figure*}

\section{Instruments for evaluation}

This work is supported by two \emph{nipype Workflows} in order to ensure the reproducibility
  of the results.
All the intermediate results and figures in this paper have been encapsulated into
  the workflows and are available in \url{http://dx.doi.org/zenodolink}.

An overview of the general workflow is presented in the Figure 2 of the paper.
However, this figure has been extremely simplified for the best of visualization.
In this section, we review the main elements of the evaluation pipelines.

\subsection{Preprocessing}

\subsection{Distortion}

\section{Model considerations}

\begin{figure*}[!ht]
	\includegraphics[width=\textwidth]{figures/Suppl-figure01.pdf}
	\caption{Evaluating the joint distribution}\label{fig:jointplot}
\end{figure*}

>>>>

% @Author: Oscar Esteban
% @Date:   2015-02-20 15:40:09
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-04-08 13:07:44

@@

% *** GRAPHICS RELATED PACKAGES ***
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{ifpdf}
\graphicspath{{figures/},{supplemental/}}

@@

% *** FLOAT PACKAGES ***
\usepackage{floatrow}
\usepackage[framemethod=tikz]{mdframed}
%\usepackage{float}
% \usepackage{fixltx2e}
% \usepackage{stfloats}
% \usepackage{dblfloatfix}

@@

\usepackage[hyphens]{url}
\usepackage[hyphenbreaks]{breakurl} %fixes boxes spanning through pages
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
\usepackage{doi}

@@

\begin{document}
\title{Supplemental Materials: \\ \emph{Active-contours driven registration method for structure-informed segmentation of diffusion MR images}}
\author{Oscar Esteban and Dominique Zosso}
\date{February 2015}

@@

\subsection{Gradient-descent optimization}\label{sec:gradient_descent}
The energy functional to be optimized in \emph{regseg} is presented in Eq. 7.
After the simplifications described in equation (A.1) of Appendix 1, we obtain the
  following energy functional:
  \begin{equation}
  E(\vec{u}) = C + \underbracket{\underset{l}{\sum} \int_{\Omega_l}
  \mdist{f'}{l} \,d\vec{r}}_{\text{Data term } (E_{data})}
  + \underbracket{\underset{\Omega}{\int} \left[ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} \right] \,d\vec{r}}_{\text{Regularization term } (E_{reg})}.
  \label{eq:energy}
  \end{equation}

To search for the minimum of $E(\vec{u})$ w.r.t. the coefficients $\vec{u}_k$, we use a gradient descent strategy.
In Eq. (9) we introduced the derivative of \eqref{eq:energy}:
  \begin{equation}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} =
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \underset{l}{\sum} \int_{\Omega_l} \mdist{f'}{l} \,d\vec{r}
  + \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\}.
  \label{eq:gradient_descent}
  \end{equation}

@@

It is also necessary to obtain and discretize the derivatives of the regularization term of \eqref{eq:gradient_descent}:
  \begin{equation}
  \frac{\partial E_{reg}(\vec{u})}{\partial \vec{u}_k} = \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\} = \boldsymbol{\alpha} \cdot \vec{u}_k - \boldsymbol{\beta} \cdot \Delta \vec{u}_k.
  \label{eq:gradient_regterm}
  \end{equation}

Inserting \eqref{eq:shape_gradient_final} and \eqref{eq:gradient_regterm} into \eqref{eq:gradient_descent} we get the
  final evolution equation:
  \begin{align}
  \frac{\partial \vec{u}}{\partial t} &\propto - \frac{\partial E(\vec{u})}{\partial \vec{u}_k}, \notag\\
  \frac{\partial \vec{u}}{\partial t} &\propto - \Big( \vec{g}_k - \boldsymbol{\alpha} \cdot \vec{u}_k + \boldsymbol{\beta} \cdot \Delta \vec{u}_k \Big).
  \label{eq:gradient_final}
  \end{align}

\subsection{Obtaining the update equation} To solve the differential equation in \eqref{eq:gradient_final},
  we use a semi-implicit Euler scheme, referring to the discrete step size as $\delta$ and where the
  shape-gradients $\vec{g}_k$ are explicit:
\begin{align}
  \vec{u}_k^{t+1} &= \vec{u}_k^{t} + \delta \, \Big( - \vec{g}_k^{t} - ( \boldsymbol{\alpha} - \boldsymbol{\beta} \Delta) \, \vec{u}_k^{t+1} \Big) \notag \\
  (1 + \delta \, \boldsymbol{\alpha} - \delta \, \boldsymbol{\beta} \Delta)\, \vec{u}_k^{t+1} &= \vec{u}_k^{t} - \delta\, \vec{g}_k^{t}
  \label{eq:discrete_derivative}
\end{align}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t - \vec{g}_k^t\} }%
                  {\mathcal{F}\{(\delta^{-1} + \boldsymbol{\alpha})\, I-\boldsymbol{\beta}\Delta\}} \right\},
  \label{eq:update_equation}
  \end{align}
  where $I$ denotes the identity operator.
Here, we rewrite the Laplacian as a linear combination of the identity and shift operators:
  \begin{equation}
  \Delta = \Big\{\sum_{d=1}^n \mathcal{S}_d^- + \mathcal{S}_d^+\Big\}  - 2n \mathcal{I}
  \end{equation}
  where $\mathcal{S}_d^{\pm}$ stands for the forward ($+$) and backward ($-$) shift operator along axis $d$, of which the Fourier transform is found easily as
  \begin{equation}
  \mathcal{F}\{\mathcal{S}_d^{\pm}\} = e^{\pm i\omega_d},
  \end{equation}
  where $\omega_d$ is the normalized pulsation along direction $d$.
Accordingly, the Fourier transform of the discrete Laplacian is found as
  \begin{align}
  \mathcal{F}\{\Delta\} &= \sum_d e^{-i\omega_d} + e^{i\omega_d} - 2n = n \, \left( \sum_d \cos(\omega_d) - 2\, \right)
  \end{align}

@@

\newpage
\section{Parameter settings and implementation details of \emph{regseg}}

@@

\subsection{Assessment of the segmentation model}
\begin{figure}[!ht]
  \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=0.5\textwidth}}]{figure}[\FBwidth]
  {\caption{\textbf{Assessment of the segmentation model}: 
  Preliminarily, we investigated the aptness of the segmentation model.
  For five test datasets, we uniformly sampled the space of distortions
    $\hat{U} = \epsilon \cdot U_{true} = \vec{r} + \epsilon \, u_\text{PE}$
    (with $\epsilon \in [-1.1, 1.1]$ and $u_\text{PE}$ from Equation 13 in the
    paper), and evaluated the data-term of the cost function \eqref{eq:energy}.
  The metric consistently displayed its minimum at the ground-truth location ($\epsilon=0.0$)
    for all the cases, indicating that the segmentation model is appropriate for
    registration.}}
  {\includegraphics[width=\linewidth]{Suppl-figure04.pdf}}
  \label{fig:energymap}
\end{figure}

@@

\begin{figure*}[b]
  \includegraphics[width=\linewidth]{Suppl-figure02.pdf}
  \caption{The evolution of the registration and segmentation process can be
    checked using the \emph{Convergence report},
    easily generated using the appropriate \emph{nipype Interface}.
  The report comprehends several plots tracking the evolution of the algorithm and several
    features to help researchers tune up the algorithm in their application.}%
    \label{fig:convreport}
\end{figure*}

\newpage
\section{Instruments for evaluation}

This work is supported by two \emph{nipype Workflows} in order to ensure the reproducibility
  of the results.
All the intermediate results and figures in this paper have been encapsulated into
  the workflows and are available in \citep{esteban_acweregistration_2015}.

An overview of the workflow applied in phantoms is presented in the Figure 2 of the paper.
Subsequently, Figure 3 reproduces the evaluation on real data.
The two figures have been extremely simplified for the best of visualization.
In this section, we review the main elements of the evaluation pipelines.

\subsection{Extraction of structural information}
\begin{figure}[!ht]
  \includegraphics[width=\linewidth]{surfaces.pdf}
  \caption{\textbf{Generating Surfaces}.
  Each surface extracted in the structural reference
    (in both phantoms and real datasets) is obtained with a unitary pipeline,
    for instance, the \emph{PialSurface} block.
  In this figure, the composite workflow to extract the six surfaces that define the
    segmentation model (\autoref{fig:jointplot}) is represented.
  }\label{fig:wf_surfaces}
\end{figure}

\subsection{Processing diffusion MRI data}
\begin{figure}[!ht]
  \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=.5\linewidth}}]{figure}[\FBwidth]
  {\includegraphics[width=.9\linewidth]{wf_dti.pdf}}
  {\caption{\textbf{Workflow to generate \gls*{fa} and \gls*{adc} maps from \gls*{dmri} data}.
    We use \emph{MRtrix} \citep{tournier_mrtrix_2012} to generate a \gls*{dti} from data and
      computing the two feature maps of interest (\gls*{fa} and \gls*{adc}).
    This workflow is performed in both undistorted and warped data.}\label{fig:wf_dti}}
\end{figure}

\subsection{T2-weighted registration to \emph{b0} -based (T2B) method}
\begin{figure}[!ht]
  \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=0.3\textwidth}}]{figure}[\FBwidth]
  {\includegraphics[width=.85\linewidth]{wf_t2b.pdf}}
  {\caption{\textbf{In-house implementation of the T2B method}.
    Each surface extracted in the structural reference
      (in both phantoms and real datasets) is obtained with a unitary pipeline,
      for instance, the \emph{PialSurface} block.
    In this figure, the composite workflow to extract the six surfaces that define the
      segmentation model (\autoref{fig:jointplot}) is represented.}\label{fig:wf_t2b}}
\end{figure}

\subsection{Complete workflow for evaluation on real data}
\begin{figure}[!ht]
  \includegraphics[width=\linewidth]{hcp_wf.pdf}
  \caption{\textbf{The \emph{nipype} design of the workflow for real data}.}\label{fig:wf_hcp}
\end{figure}

\newpage
\section{Model considerations}

\begin{figure*}[!ht]
	\includegraphics[width=\linewidth]{Suppl-figure01.pdf}
	\caption{Evaluating the joint distribution}\label{fig:jointplot}
\end{figure*}
